\begin{thebibliography}{99}
\bibitem{lsm} Diego Restrepo, Hac\'\i a la teor\'\i a cu\'antica de campos, curso web, \url{http://gfif.udea.edu.co}

\bibitem{Maggiore:2005qv}
  M.~Maggiore,
  ``A Modern introduction to quantum field theory,''
%\href{http://www.slac.stanford.edu/spires/find/hep/www?irn=6374123}{SPIRES entry}
{\it  Oxford University Press, 2005. (Oxford Series in Physics, 12. ISBN 0 19 852073 5)}

\bibitem{Mandl:1985bg}
  F.~Mandl and G.~Shaw,
  %``Quantum Field Theory,''
%\href{http://www.slac.stanford.edu/spires/find/hep/www?irn=1457594}{SPIRES entry}
{\it  Chichester, Uk: Wiley ( 1984) 354 P. ( A Wiley-interscience Publication)}

\bibitem{Lahiri:2005sm}
  A.~Lahiri and P.~B.~Pal,
  ``A first book of quantum field theory,''
%\href{http://www.slac.stanford.edu/spires/find/hep/www?irn=6927483}{SPIRES entry}
  {\it  Harrow, UK: Alpha Sci. Int. (2005) 380 p}


\bibitem{Pal:2007dc}
P.~B.~Pal,
``Representation-independent manipulations with Dirac spinors,''
[arXiv:physics/0703214 [physics.ed-ph]].
%20 citations counted in INSPIRE as of 18 Nov 2020

\bibitem{physics/0703214} Pal, P. ``Representation-independent manipulations with Dirac matrices and spinors'',
	arXiv:physics/0703214v2 [physics.ed-ph]

\bibitem{Langacker:2010zza}
P.~Langacker,
``The standard model and beyond,''
%66 citations counted in INSPIRE as of 18 Nov 2020

\bibitem{Larkoski:2019jnv}
A.~J.~Larkoski,
``Elementary Particle Physics: An Intuitive Introduction,''
%0 citations counted in INSPIRE as of 18 Nov 2020

        
\bibitem{PD} Wikipedia article: \url{http://en.wikipedia.org/wiki/Particle_decay}

\bibitem{Klasen:2002xi}
  M.~Klasen,
  %``Calculating two- and three-body decays with FeynArts and FormCalc,''
  Int.\ J.\ Mod.\ Phys.\  C {\bf 14} (2003) 1273
  [arXiv:hep-ph/0210426].
  %%CITATION = IMPAE,C14,1273;%%

\bibitem{PeterRenton} \emph{Electroweak Interactions}, Peter Renton


\bibitem{Peskin}
Michael E. Peskin and Daniel V. Schroeder. \emph{An introduction to
Quantum Field Theory}, Addison-Wesley Publishing Company(1995), p.
101

\bibitem{Peskin1}
ibdg 1, p. 105

\bibitem{Halzen}
Francis Halzen and Alan D. Martin. \emph{Quarks} \& \emph{Leptons:
An introductory Course in Modern Particle Physics}, John Wiley \&
Sons(1984), p. 89

\bibitem{Quigg}
Chris Quigg. \emph{Gauge theory of the Strong, Weak and
Electromagnetic Interactions}, Westview Press(1997), p. 110


\bibitem{Quigg1}
ibdg 4, p. 130.

\bibitem{Mandl1}
ibdg 5, p. 325.


\bibitem{Sierra:2008wj}
  D.~Aristizabal Sierra, J.~Kubo, D.~Restrepo, D.~Suematsu and O.~Zapata,
  ``Radiative seesaw: Warm dark matter, collider and lepton flavour violating
  signals,''
  Phys.\ Rev.\  D {\bf 79} (2009) 013011
  [arXiv:0808.3340 [hep-ph]].
  %%CITATION = PHRVA,D79,013011;%%

\bibitem{Gross:1993} 
Relativistic Quantum Mechanics and Field Theory, Franz Gross, John Wiley \& Sons, INC. 1993

\bibitem{McMahon:2009zz}
  D.~McMahon,
  ``Quantum field theory demystified: A self-teaching guide,''
  \href{http://www.slac.stanford.edu/spires/find/hep/www?irn=8432112}{SPIRES entry}
{\it  New York, USA: McGraw-Hill (2009) 299 p}

\bibitem{Feynman:1986er}
  R.~P.~Feynman,
  ``QED. The Strange Theory Of Light And Matter,''
%\href{http://www.slac.stanford.edu/spires/find/hep/www?irn=1631209}{SPIRES entry}
{\it  Princeton, Usa: Univ. Pr. ( 1985) 158 P. ( Alix G. Mautner Memorial Lectures)}


\bibitem{Semenov:2008jy}
  A.~Semenov,
  ``LanHEP - a package for the automatic generation of Feynman rules in field
  theory. Version 3.0,''
  Comput.\ Phys.\ Commun.\  {\bf 180} (2009) 431
  [arXiv:0805.0555 [hep-ph]], \url{http://feynrules.phys.ucl.ac.be/}.
  %%CITATION = CPHCB,180,431;%%

\bibitem{Christensen:2008py}
  N.~D.~Christensen and C.~Duhr,
  ``FeynRules - Feynman rules made easy,''
  Comput.\ Phys.\ Commun.\  {\bf 180}, 1614 (2009)
  [arXiv:0806.4194 [hep-ph]],
   \url{http://feynrules.phys.ucl.ac.be/}.
  %%CITATION = CPHCB,180,1614;%%

\bibitem{massivephoton}
  Christianto V., Smarandache F., and Lichtenberg F., 
  ``\href{http://www.ptep-online.com/index_files/2009/PP-16-08.PDF}{A Note of Extended Proca Equations and Superconductivity,}''
  Progress in Physics, \textbf{1} (2009) 40
  [viXra:1003.0054]

\bibitem{Martin}Martin, Many body quantum field theory

\bibitem{Dreiner:2008tw}
  H.~K.~Dreiner, H.~E.~Haber and S.~P.~Martin,
  ``Two-component spinor techniques and Feynman rules for quantum field theory and supersymmetry,''
  Phys.\ Rept.\  {\bf 494} (2010) 1
  doi:10.1016/j.physrep.2010.05.002
  [arXiv:0812.1594 [hep-ph]].
  %%CITATION = doi:10.1016/j.physrep.2010.05.002;%%
  %185 citations counted in INSPIRE as of 18 May 2016

\bibitem{Roncadelli:1983ty}
  M.~Roncadelli and D.~Wyler,
  ``Naturally Light Dirac Neutrinos in Gauge Theories,''
  Phys.\ Lett.\  {\bf 133B} (1983) 325.
  doi:10.1016/0370-2693(83)90156-9
  %%CITATION = doi:10.1016/0370-2693(83)90156-9;%%
  %84 citations counted in INSPIRE as of 30 Mar 2018
  
\bibitem{Suematsu:2017kcu}
  D.~Suematsu,
  ``Dark matter stability and one-loop neutrino mass generation based on Peccei–Quinn symmetry,''
  Eur.\ Phys.\ J.\ C {\bf 78} (2018) no.1,  33
  doi:10.1140/epjc/s10052-018-5519-4
  [arXiv:1709.02886 [hep-ph]].
  %%CITATION = doi:10.1140/epjc/s10052-018-5519-4;%%
  %5 citations counted in INSPIRE as of 21 Aug 2019

  
\end{thebibliography}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "beyond"
%%% End: